---
title: "525 Final Project"
author: "Pallava Arasu Pari"
date: "4/12/2020"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Set Path and Load libraries
```{r}
setwd("~/Harrisburg/525")
library(Quandl)
library(readxl)
library(FRAPO)
library(timeSeries)
library(QRM)
library(fGarch)
library(readr)
library(zoo)
library(fBasics)
#library(fitdistrplus)
library(forecast)
```


#Load Data
```{r}
#data from bombday exchange market

#Indian Oil Corporation
IOC<-Quandl("BSE/BOM530965", start_date="2015-01-01")

#Tata Steel
tata_Stell<-Quandl("BSE/BOM500470", start_date="2015-01-01")

#Infosys is a leading Information Technolgy firm
infosys<-Quandl("BSE/BOM500209", start_date="2015-01-01")
```


# Data Exploration
```{r}
date<-IOC$Date

IOCClose<-IOC$`Close`
TataSteelClose<-tata_Stell$`Close`
InfosysClose<-infosys$`Close`

attr(IOCClose, 'time')<-date
attr(TataSteelClose, 'time')<-date
attr(InfosysClose, 'time')<-date

datechar<-as.character(IOC$Date)
```

Trasnformations
```{r}
library(timeSeries)
#combining data
assets<-cbind(IOCClose,TataSteelClose,InfosysClose)
#timeseries
asseststs<-timeSeries(assets,charvec = datechar)
plot(asseststs)
```

Calculating Loss
```{r}
assestsLoss<-as.data.frame(na.omit(-1.0*diff(log(asseststs))*100.0))
assestsLossts<-timeSeries(assestsLoss)
plot(assestsLossts)
head(assestsLoss)
IOCCloseLossMean=mean(assestsLossts$IOCClose)
TataSteelCloseLossMean=mean(assestsLossts$TataSteelClose)
InfosysCloseLossMean=mean(assestsLossts$InfosysClose)
IOCCloseLossMean
TataSteelCloseLossMean
InfosysCloseLossMean
```


Calculating returns
```{r}
assetsReturns<-na.omit(returnseries(asseststs, method = "discrete",trim = FALSE))
plot(assetsReturns)
IOCReturnsMean=mean(assetsReturns$IOCClose)  
IOCReturnsMean  #0.1775025
TataSteelReturnsMean=mean(assetsReturns$TataSteelClose)  
TataSteelReturnsMean   #0.05557905
InfosysReturnsMean=mean(assetsReturns$InfosysClose) 
InfosysReturnsMean #0.1465191

```

`r max(IOCReturnsMean,TataSteelReturnsMean,InfosysReturnsMean)` offers the highest expected return


acf and pacf 
```{r}
par(mfrow=c(3,2), mar = c(4,4,4,4) ) 

IOC
acf(assestsLossts$IOCClose, main="ACF of IOC Losses" , lag.max=20, ylab="", xlab= "", col="blue", ci.col="red") 
pacf(assestsLossts$IOCClose, main="PACF of IOC Losses" , lag.max=20, ylab="", xlab= "", col="blue", ci.col="red") 

##Tata Steel
acf(assestsLossts$TataSteelClose, main="ACF of Tata Steel Losses" , lag.max=20, ylab="", xlab= "", col="blue", ci.col="red") 
pacf(assestsLossts$TataSteelClose, main="ACF of Tata Steel Losses" , lag.max=20, ylab="", xlab= "", col="blue", ci.col="red") 

##Infosys
acf(assestsLossts$InfosysClose, main="ACF of Infosys Losses" , lag.max=20, ylab="", xlab= "", col="blue", ci.col="red") 
pacf(assestsLossts$InfosysClose, main="ACF of Infosys Losses" , lag.max=20, ylab="", xlab= "", col="blue", ci.col="red") 
```

#Arima

Find Order of Arima
```{r}
#Rank of IOC arima model:
arimaIOC=auto.arima(assestsLossts$IOCClose)#000
arimaIOC

#Rank of Tata Steel arima model:
arimaTataSteel=auto.arima(assestsLossts$TataSteelClose)#203
arimaTataSteel

#Rank of Infoys arima model:
arimaInfosys=auto.arima(assestsLossts$InfosysClose)#302
arimaInfosys

```

Function for Expected Shortfall measure of risk with 95 %
```{r}
ESgarch <- function(y,asset=1, p = 0.95){
  gfitIOC =garchFit(formula = ~arma(0,0,0)+garch(1, 1), data = y,
                   cond.dist = "std", trace = FALSE)
  gfitTataSteel =garchFit(formula = ~arma(2,0,3)+garch(1, 1), data = y,
                   cond.dist = "std", trace = FALSE)
  gfitInfosys=garchFit(formula = ~arma(3,0,2)+garch(1, 1), data = y,
                   cond.dist = "std", trace = FALSE)
  gfit<-switch (asset,gfitIOC,gfitTataSteel,gfitInfosys)

  sigma <-  as.numeric(predict(gfit, n.ahead = 1)[3])
  df <- as.numeric(coef(gfit)["shape"])
  ES <- sigma * (dt(qt(p, df), df)/(1 - p)) *
    ((df + (qt(p, df))^2)/(df - 1))
  return(ES)
}

```
#Garch
ES for the individual assests
```{r}
#ES of IOC
ESGarchIOC=ESgarch(assestsLossts$IOCClose,asset=1)
ESGarchIOC

#ES of Tata Steel
ESGarchTataSteel=ESgarch(assestsLossts$TataSteelClose,asset=2)
ESGarchTataSteel

#ES of Infosys
ESGarchInfosys=ESgarch(assestsLossts$InfosysClose,asset=3)
ESGarchInfosys

```
Estimated Shorfall measure of Risk with 95% CI for IOC is `r ESGarchIOC`, Tata Steel is `r ESGarchTataSteel` and Infosys is `r ESGarchInfosys`

`r c('IOC','Tata Steel','Infosys')[which.max(c(ESGarchIOC,ESGarchTataSteel,ESGarchInfosys))]` has the highest overall risk with 95% confidance.



Covariance Martrix on Returns
```{r}
assetscov <-cov(assetsReturns, use="pairwise.complete.obs")
assetscov
```

We worry more about the risk than the profit. So lets check out the Global Minimum Variance Portfolio
```{r}
GMVP<-PGMV(assetscov,percentage = TRUE)
w<-Weights(GMVP)
GMVPwIOC<-as.numeric(w[1])
GMVPwIOC   # 15.40196
GMVPwTataSteel<-as.numeric(w[2])
GMVPwTataSteel   # 64.74288
GMVPwInfosys<-as.numeric(w[3])
GMVPwInfosys # 19.85516

```
```{r}
Weights(GMVP)

```
